\section{One-way Functions}
\begin{enumerate}[(a)]
	\item Let $G: \bits^\lambda \to \bits^{2\lambda}$ be a PRG with $\lambda$-bit stretch. Prove that $G$ is by itself a one-way function.

	      \begin{solution}
		      \begin{cryptoredux}
			      {3.a}
			      {Base an attack to PRG $G$, assuming the existence of a PPT attacker $\mathcal{A}$, able to find pre-images of $G$ with non-negligible probability. $\mathcal{A}^*$ returns a bit $b$ to the challenger $\mathcal{C}$, in order to distinguish.}
			      {}
			      {}
			      {}
			      \receive{\shortstack[l]{
					      $y \casesnew{-stealth}{\ud \bits^{2\lambda}}{G(x), x \ud \bits^\lambda}$
				      }}
			      {$y$}{}
			      \invoke{}{$y$}{}
			      \return{}{$x'$}{}
			      \cseqdelay
			      \send{$b = \begin{cases}
						      1 & \textsc{iff } G(x') = y \\
						      0 & \textsc{else}
					      \end{cases}$
			      }{$b$}{}
		      \end{cryptoredux}
		      Assume G is not a OWF: then there exists some PPT attacker $\mathcal{A}$ able to find a pre-image $x'$ of input values $y$ (see figure \ref{cryptoredux:3.a}).
		      Let us define \underline{valid}\footnote{just a shortcut to indicate that $y \in G(\cdot)$.} an input $y$ if $\exists x: G(x) = y$.

		      We have that $\P[\mathcal{A}(y) = 1: x \ud \bits^\lambda; y = G(x)] \ge \frac{1}{p(\lambda)}$, for some $p(\lambda) \in poly(\lambda)$ for hypothesis.
		      Moreover, the probability that a random $2\lambda$ bits string is valid is at most equal to the ratio between the number of valid inputs and the number of possible inputs: this ratio is equal to $\frac{2^\lambda}{2^{2\lambda}} = 2^{-\lambda}$.
		      From which we derive that $\P[\mathcal{A}(y) = 1: y \ud \bits^{2\lambda}] \le 2^{-\lambda}$.
		      So we have:
		      \[\P[\mathcal{A}(y) = 1: x \ud \bits^\lambda; y = G(x)] - \P[\mathcal{A}(y) = 1: y \ud \bits^{2\lambda}] \ge \frac{1}{p(\lambda)} - 2^{-\lambda} \notin negl(\lambda) \]
	      \end{solution}

	\item Let $f: \bits^n \to \bits^n$ be a OWF. Consider the function $g: \bits^{n + \log{n}} \to \bits^{n + \log{n} + 1}$ defined by $g(x||j) \deq (f(x), j, x_j)$, where $x \deq (x_1, \dots, x_n)$, and $j$ is interpreted as an integer in $[n]$ (i.e. $|j| = \log n$).

	      \begin{enumerate}[(i)]
		      \item Show that $g$ is an OWF if $f$ is.

		            \begin{solution}
			            Assume not. Then there exists a PPT attacker $\mathcal{A}$ able to invert $g$ with non negligible probability: if so, we show that we can break $f$ too (see figure \ref{cryptoredux:3.b.1}).
			            \begin{cryptoredux}
				            {3.b.1}
				            {Base an attack to OWF $f$, assuming the existence of a PPT attacker $\mathcal{A}$, able to invert $g$ with non negligible probability. $\mathcal{A}^*$ wins the game if it finds a value $x'$ such that $f(x') = y$ provided by the challenger $\mathcal{C}$.}
				            {}
				            {}
				            {}
				            \receive{\shortstack[l]{
						            $x \ud \bits^n$ \\
						            $y = f(x) $
					            }}
				            {$y$}{}
				            \cseqdelay
				            \invoke{\shortstack[l]{
						            $j \ud [n]$ \\
						            $x'_j \ud \bits $
					            }}{$y || j || x'_j$}{}
				            \cseqdelay
				            \return{}{$x'$}{}
				            \send{}{$x'$ \textsc{iff } f(x') = y}{}
				            \invoke{}{$y || j || (x'_j \xor 1)$}{}
				            \return{}{$x'$}{}
				            \send{}{$x'$}{}
			            \end{cryptoredux}
			            Our attacker tries to guess the value for the $j$-th bit and queries $\mathcal{A}$ to find the pre-image of $y||j|x_j$. However, it could be that the guess is wrong: but we can try again, flipping the  $j$-th bit, if we realize that $f(x') \ne y$. Then, it is obvious that the probability to win the game, i.e. to find some valid pre-image of $y$ is exactly equal to the probability of finding a pre-image of a valid $y^*$ for attacker $\mathcal{A}$: and this is non-negligible by assumption.
		            \end{solution}

		      \item Show that for every $i \in [n']$ there is a PPT algorithm $A_i$ for which
		            \[ \P[A_i(g(x')) = x_i' : x' \ud \bits^{n + \log{n}}] \ge \frac{1}{2} + \frac{1}{2n}\]
		            where $x' = (x_1, \dots, x_{n'})$

		            \begin{solution}
			            Let $y \in \bits^{n + \log{n}}, y' \in \bits^n, j \in \bits^{\log n}$.

			            We define $A_i(y) = A_i(y'||j||\cdot) = \begin{cases}
					            y_i & \textsc{if } i > n \vee i = j \\
					            0   & \textsc{else}
				            \end{cases}$

			            Then we can prove that $\P[A_i(g(x')) = x_i' : x' \ud \bits^{n + \log{n}}] \ge \frac{1}{2} + \frac{1}{2n}$

			            First of all, $A_i$ is a PPT $\forall i$, since it only parses the input string, whose length is $n + \log{n} + 1$.
			            As for the bound, for all indexes $i > n$ (i.e. the last $\log{n}$ bits) $A_i$ finds the correct value, because it is embedded in the input.
			            For all other indexes, there are two cases: if $i = j$ (this happens with probability = $1/n$) $A_i$ returns the correct value with probability 1 (again, the value is visible to the attacker); if $i \ne j$ (with probability $\frac{n-1}{n}$) $A_i$ can at least guess (returning 0) and win with probability $\frac{1}{2}$. If we take the weighted average we prove the bound also for $i \le n$, since:
			            \[\forall i \le n,\; \P[A_i(g(x')) = x_i' : x' \ud \bits^{n + \log{n}}] \ge \frac{1}{n} + \frac{n-1}{2n} = \frac{1}{2} + \frac{1}{2n} \]
		            \end{solution}
	      \end{enumerate}
\end{enumerate}